---
title: "export LAS files of training and test trees"
author: "MÅM"
date: "2023-12-21"
output: html_document
---

Aim: export LAS files of MLS point clouds of training and test trees using their coordinates. 
Output: files in R:\\Data\\VaalerIIII\\2023\\MLS\\test_train_segmented\\test_automatic_segmentation\\
files in R:\\Data\\VaalerIIII\\2023\\MLS\\test_train_segmented\\train_automatic_segmentation\\
files in S:\\Users\\maria\\Paper_3\\data\\fielddata\\domtree_positions_man_seg\\test\\
files in S:\\Users\\maria\\Paper_3\\data\\fielddata\\domtree_positions_man_seg\\train\\


```{r}
library(lidR)
library(tidyverse)
library(data.table)
library(rgl)
setwd("S:\\Users\\maria\\Paper_3\\")
```


# Test data

## Import test data 

```{r}
test_coord_files = list.files("data/test_trees/coordinates")
test_coord = bind_rows(map(test_coord_files, ~ read.table(paste0("data/test_trees/coordinates/", .x), sep = ",", header = F)))

colnames(test_coord) = c("x", "y", "z", "TreeID", "SegmentedID", "plotname")
test_coord = as.data.table(test_coord)

test_coord[is.nan(as_vector(test_coord[,"SegmentedID"])), "SegmentedID"] <- NA # Replace NaN with NA 
```

## Make LAS files of the Segmented trees that correspond to the test trees

```{r}
test_man_seg = filter(test_coord, is.na(SegmentedID))

test_coord = test_coord[,-"z"] # I do not need the z-coordinate

test_seg = filter(test_coord, !(is.na(SegmentedID))) 

# Just for now I need to take out a few problematic observations.. 
test_seg = test_seg %>% 
  mutate(SegmentedID = as.numeric(SegmentedID))

## Looping through each plot and segmenting out trees with the Segmented ID given in the table test_seg. Saving to seperate LAZ files per tree. 

vec_plots_processed_segmented = c(2449402) # For some of the plots, I needed to use the dataset in "R:\\Data\\VaalerIIII\\2023\\MLS\\processed_segmented" because the shift in x,y was so great that the tree ended up outside the 10 meter buffer. 

i = 1

for(i in 1:length(unique(test_seg$plotname))) {
  
  test_coord_plot = test_seg %>% 
    filter(plotname == unique(test_seg$plotname)[i])
  
  if(any(test_coord_plot$plotname %in% vec_plots_processed_segmented)) {
    
    LAS_file_plot = readLAS(paste0("R:\\Data\\VaalerIIII\\2023\\MLS\\processed_segmented\\", unique(test_seg$plotname)[i],".laz"))
    
  } else {
    
      LAS_file_plot = readLAS(paste0("R:\\Data\\VaalerIIII\\2023\\MLS\\processed_segmented_clipped\\", unique(test_seg$plotname)[i],".laz"))

  }
  
  LAS_file_plot_segmented = list()
  
  for (j in 1:nrow(test_coord_plot)) {
    
    LAS_file_plot_segmented[[j]] = filter_poi(LAS_file_plot, preds_instance_segmentation == test_coord_plot$SegmentedID[j])
    
    writeLAS(LAS_file_plot_segmented[[j]], paste0("R:\\Data\\VaalerIIII\\2023\\MLS\\test_train_segmented\\test_automatic_segmentation\\", test_coord_plot$TreeID[j], ".laz"))
    
  }
  
}

```

# Train data

## Import train data

```{r}
train_coord_files = list.files("data/train_trees/coordinates")
train_coord = map(train_coord_files, ~ read.table(paste0("data/train_trees/coordinates/", .x), sep = ",", header = F))
train_coord_files_notxt = as.numeric(sub("\\.txt$", "", train_coord_files))
train_coord1 = map2(train_coord, train_coord_files_notxt, ~ .x %>% 
                      mutate(plotname = .y)) # Add the plotname 
train_coord1 = as.data.table(bind_rows(train_coord1))

colnames(train_coord1) = c("x", "y", "z", "SegmentedID", "plotname") # name (and rename) to match names in the test data 
train_coord1[is.nan(as_vector(train_coord1[,"SegmentedID"])), "SegmentedID"] <- NA # Replace NaN with NA 
```


## Make LAS files of the Segmented trees that correspond to the train trees

```{r}
train_man_seg = filter(train_coord1, is.na(SegmentedID)) 

traindata = train_coord1[,-"z"] # I don't need z

train_seg = filter(traindata, !(is.na(SegmentedID))) 

# Just for now I need to take out a few problematic observations.. 
train_seg = train_seg %>% 
  mutate(SegmentedID = as.numeric(SegmentedID))


## Looping through each plot and segmenting out trees with the Segmented ID given in the table train_seg. Saving to seperate LAZ files per tree. 

for(i in 1:length(unique(train_seg$plotname))) {
  
  train_coord_plot = train_seg %>% 
    filter(plotname == unique(train_seg$plotname)[i])
  
      LAS_file_plot = readLAS(paste0("R:\\Data\\VaalerIIII\\2023\\MLS\\processed_segmented_clipped\\", unique(train_seg$plotname)[i],".laz"))

  LAS_file_plot_segmented = list()
  
  for (j in 1:nrow(train_coord_plot)) {
    
    LAS_file_plot_segmented[[j]] = filter_poi(LAS_file_plot, preds_instance_segmentation == train_coord_plot$SegmentedID[j])
    
    writeLAS(LAS_file_plot_segmented[[j]], paste0("R:\\Data\\VaalerIIII\\2023\\MLS\\test_train_segmented\\train_automatic_segmentation\\", train_coord_plot$plotname[j], "_", j, ".laz"))
    
  }
  
}

```


# Save the positions of dominant trees to use in the manual segmentation

```{r}
length(unique(test_man_seg$plotname))
length(unique(train_man_seg$plotname))
```


```{r}
# save test tree positions for manual segmentation

test_man_seg1 = test_man_seg %>% 
  filter(!is.na(x) & !is.na(y) & !is.na(z)) # Only trees which have a measured coordinate should be considered. 

test_path = "S:\\Users\\maria\\Paper_3\\data\\fielddata\\domtree_positions_man_seg\\test\\"

for(i in 1:length(unique(test_man_seg1$plotname))) {
  
  test_file = test_man_seg1 %>% 
    filter(plotname == unique(test_man_seg1$plotname)[i])
  
  new_test_name = as.character(unique(test_file$plotname))
  
  write.table(test_file, paste0(test_path, new_test_name, ".txt"), col.names = F, row.names = F, sep = ",")
  
}

```


```{r}
# save train tree positions for manual segmentation

train_man_seg1 = train_man_seg %>% 
  filter(!is.na(x) & !is.na(y) & !is.na(z)) # Only trees which have a measured coordinate should be considered. 

train_path = "S:\\Users\\maria\\Paper_3\\data\\fielddata\\domtree_positions_man_seg\\train\\"

for(i in 1:length(unique(train_man_seg1$plotname))) {
  
  train_file = train_man_seg1 %>% 
    filter(plotname == unique(train_man_seg1$plotname)[i])
  
  new_train_name = as.character(unique(train_file$plotname))
  
  write.table(train_file, paste0(train_path, new_train_name, ".txt"), col.names = F, row.names = F, sep = ",")
  
}
```


# Import segmented clipped LAS files

```{r}
check2 = filter(testdata, !(is.na(SegmentedID))) # 49 testing trees.. 

# Just for now I need to take out a few problematic observations.. 
check2 = na.omit(check2)
check2 = check2 %>% 
  mutate(SegmentedID = as.numeric(SegmentedID))


for(i in 1:nrow(check2)) {
  
  check1 = readLAS(paste0("R:\\Data\\VaalerIIII\\2023\\MLS\\processed_segmented_clipped\\", check2[i,]$CloudProcSegID,".laz"))
  
  test = filter_poi(check1, preds_instance_segmentation == check2[i,]$SegmentedID)
  
  plot(test)
  
  rgl.postscript(paste0("S:/Users/maria/Paper_3/processing/images_of_segmented_chosen_trees/test/",check2[i,]$CloudProcSegID, "_",check2[i,]$SegmentedID,".pdf"), fmt = "pdf")
  
  # Clear the 'rgl' device
  rgl.clear()
  
}

check1 = readLAS(paste0("R:\\Data\\VaalerIIII\\2023\\MLS\\processed_segmented_clipped\\", check2[1,]$CloudProcSegID,".laz"))

check1 = readLAScatalog(paste0("R:\\Data\\VaalerIIII\\2023\\MLS\\processed_segmented_clipped\\"))

test = filter_poi(check1, preds_instance_segmentation == check2[1,]$SegmentedID)

# plot(check1, color = preds_instance_segmentation)
plot(test)
```
